RNA-seq from 4 cell populations

### 2021-07-28 deconvolution/fans4/molec_profiling.Rmd
bug fix

## Differential expression analysis
### Cell type
```{r DE_process}
form = ~ 0 + CellType + (1|Individual.ID) + (1|Gender) + (1|Batch)

@@

>>>>

## Differential expression analysis
### Cell type
```{r DE_process, eval=FALSE}
form = ~ 0 + CellType + (1|Individual.ID) + (1|Gender) + (1|Batch)

@@

idx = as.integer(seq(1, 2000, length.out=100))
lapply(2:length(idx), function(i){
  message(i, '     ')
fitBasic = dream( vobj[idx[i-1]:idx[i],], form, info, L=L, BPPARAM=SerialParam())

})

i = 173:173
fitBasic = dream( vobj[i,,drop=FALSE], form, info, L=L, BPPARAM=SerialParam())
